---
title: "NicoSchwarzer_Excercise5"
author: "Nico"
date: "31 1 2021"
output: html_document
---
---
title: "Assignment 4"
author: "Nico"
date: "02 02 2021"
output: html_document
---


## Author
By: Nico Schwarzer, 
Student-ID:5632297

## Excercise  1 

### Preparations 

I first install all necessary packages. I also set the working directory and call the file 'API_key', where my API key is hidden. 
```{r exercise 1_1, message = FALSE}

library(tidyverse)
library(jsonlite)
library(httr)
library(rlist)
library(knitr)

knitr::opts_knit$set(root.dir = 'C:/Users/Nico/Documents/Tübingen/1. Sem/DS Project Management/Exercises/E5/working_with_API')


source('C:/Users/Nico/Documents/Tübingen/1. Sem/DS Project Management/Exercises/E5/API_key.R')

```

### Connection to GitHub 

As demanded in the exercise, I have created a new GitHub repository called 'working_with_API'. It shall include a 'READ ME' file as well as the code, i.e. this document. The file, in which the API key is stored, shall not be included in this GitHub project. 

The link to the GitHub repository is: https://github.com/NicoSchwarzer/working_with_API . 



## Excercise 2 

On the given website, one can find different APIs. The "Discovery API" is of interest to us. This API has limits of 5000 API calls per day and rate limitation of 5 requests per second. That is why one should not run this file multiple time per day! Also, I have included a 'Sys.sleep(0.2)' command in all loop statements below, which ensures that no more than 5 request will be run per second. I have retrieved an API key from the "API Explorer" and stored it in a different file, which I would have to run first. Here, it is simply referred to as "key_1". 



## Excercise 3 

For aesthetic reasons, I have already installed all required packages in the beginning of this RMD-file. 

### GET-request for German event venues 

I use the hidden API key to retrieve the data. I first check the status code to make sure that the code works properly. Since the status is 200, the latter is the case here. I then use the 'content' command to load the content. I then transfer the data into an R list, which is stored in 'content_1'. It is a list of three and contains the sub-lists "_embedded", "_page" and "links". To construct a dataframe, one needs to retrieve data via 'content_1$'_embedded'$events'. I am storing the data in the datafame 'content_1_df'.

```{r exercise 3_1, message = FALSE}



get_1 <- GET("https://app.ticketmaster.com/discovery/v2/events/",
              query = list(apikey = key_1,
                           countryCode = "DE")) 


print(get_1$status_code)

content_1 <- content(get_1, as  = "text")

content_1 <- fromJSON(content_1)

content_1_df <- data.frame(content_1$'_embedded'$events)

```

### Extracting certain variables 

The variables 'name' and 'url' can be taken directly from the above-mentioned dataframe. All other variables need to be retrieved via the dataframes contained in the DF content_1_df. All the required variables are then added to the new dataframe 'venue_data'. Furthermore, I set all empty entries to NA, so that the plotting will not results in any difficulties as one can simply ignore/remove NA-entrys then. 

```{r exercise 3_2, message = FALSE}

# Keeping name & url
venue_data <- content_1_df %>%
  select(name, url)

## Retrieving more data:

#city
cities <- rep(0, 20)

for (i in 1:20) {
  if (is.null(content_1_df$X_embedded[1]$venues[[i]]$city$name)) {
    cities[i] <- NA
  } else {
    cities[i] <- content_1_df$X_embedded[1]$venues[[i]]$city$name
}}


# postal code
postal_codes <- rep(0, 20)

for (i in 1:20) {
  if (is.null(content_1_df$X_embedded[1]$venues[[i]]$postalCode)) {
    postal_codes[i] <- NA
  } else {
 postal_codes[i] <- content_1_df$X_embedded[1]$venues[[i]]$postalCode
}}


# address
ad <- rep(0, 20)

for (i in 1:20) {
  if (is.null(content_1_df$X_embedded[1]$venues[[i]]$address$line1)) {
    ad[i] <- NA
  } else {
ad[i] <-  content_1_df$X_embedded[1]$venues[[i]]$address$line1
}}


# longitude
long <- rep(0, 20)

for (i in 1:20) {
  if ( is.null(content_1_df$X_embedded[1]$venues[[i]]$location$longitude)) {
    long[i] <- NA
  } else {
  long[i] <- content_1_df$X_embedded[1]$venues[[i]]$location$longitude
  } 
}

  
# 5 
# latitude 
lat <- rep(0, 20)

for (i in 1:20) {
  if (is.null(content_1_df$X_embedded[1]$venues[[i]]$location$latitude)) {
    lat[i] <- NA
  } else {
lat[i] <- content_1_df$X_embedded[1]$venues[[i]]$location$latitude
}}


## Enlarging the new dataframe 
venue_data$city <- cities
venue_data$postalCode <- postal_codes
venue_data$address <- ad
venue_data$longitude <- long
venue_data$latitude <- lat


venue_data$longitude <- as.double(venue_data$longitude)
venue_data$latitude <- as.double(venue_data$latitude)

venue_data_DE <- venue_data

glimpse(venue_data_DE)

```

